Introduction to Lattice-based Attacks\\``Cryptography''

### 2021-06-07 lattice_based_attacks.tex
Rename repository and paper
Update conclusions

The lattice-based attacks presented here are based on the \textit{Hidden Number Problem} introduced
by Boneh and Venkatesan \cite{hnp} that was in a second moment generalized to prove that the most significan bits
of $k$ can potentially leak the entire nonce \cite{ecdsa_nonce}.

@@

\textbf{Problem setup}.
Let $p = \texttt{0xffffffffffffd21f}$ and let $E: y^2 = x^3 + 3$ be an elliptic curve over $\F_p$ with the generator
$G = (\texttt{0xcc3b3d1a0c4938ef}, \texttt{0x4ab35ff66f8194fa})$ of order $n = \texttt{0xfffffffefa23f437}$.

@@

Without any optimization we were able to recover the nonces with the $10$ MSB bits known on the curve \texttt{secp256r1} given $100$ signatures,
but it's also possible to recover the nonces with less known bits as shown in the results obtained by Albrecht and Heninger \cite{ecdsa_result}.

@@

$gg^2$

\bibliographystyle{plain}
\bibliography{paper}

>>>>

The lattice-based attacks presented here are based on the \textit{HNP (Hidden Number Problem)} introduced
by Boneh and Venkatesan \cite{hnp} that was in a second moment generalized to prove that the most significan bits
of $k$ can potentially leak the entire nonce \cite{ecdsa_nonce}.
In 2020 a group of researcher were able to leak the MSBs of \textit{DH} and \textit{DHE} secrets in \textbf{TLS $\le$ 1.2}
and using a similar lattice constructions as the one we will describe to solve the \textit{HNP}
and thus breaks the protocol \cite{cryptoeprint:2020:1151} (Raccoon Attack).

@@

\textbf{Problem setup}.
Let $p = \texttt{0xffffffffffffd21f}$ and let $E: y^2 = x^3 + 3$ be an elliptic curve over $\F_p$ with the generator
$G = (\texttt{0xcc3b3d1a0c4938ef}, \\ \texttt{0x4ab35ff66f8194fa})$ of order $n = \texttt{0xfffffffefa23f437}$.

@@

Without any optimization we were able to recover the nonces with the $8$ MSB bits known on the curve \texttt{secp256r1} given $100$ signatures 
and with a probability bigger than $50\%$ with $7$ MSB bits known.

It's possible to optimize the attack to recover the nonces with less known bits as shown in the results obtained by
Albrecht and Heninger \cite{ecdsa_result}.

@@

The results obtained from the implementation of the attacks are satisfactory and can be used against real world practical cases.
There is a fair amount of probability and heuristic to make the attacks works that isn't discussed in detail.
As with other branch of mathematics not all theorems and properties are proved to be useful the moment they were first introduced
but can become useful years later as the hidden number problem that become crucial for the Raccoon Attack.
The study on how to exploit side-channel attacks (ex. knowing some bits of $p$ in \textbf{RSA}) has been proven useful
with \textbf{ROCA}.
The most used cryptographic protocol used has been proved secure but it's very easy to implement them wrong and side-channel
vulnerabilities can heavily compromise the security of the protocol.

\bibliographystyle{plain}

\bibliography{lattice_based_attacks}
